---
title: "Case Studies"
author: "Jolien De Clercq"
date: "2023-05-01"
output: html_document
---

```{r, packages, message = FALSE}
# loading packages
library(readxl)
library(lavaan)
library(QuantPsyc)
library(semTools)
library(diagram)
library(WebPower)
library(car)
```

```{r, import and manipulate data}
# reading in dataset
data1 <- read_excel('dataset_study1_OSF.xlsx')
data2 <- read_excel('dataset_study2_OSF.xlsx')

# remove extra columns in data2 
data2$CI  = NULL
data2$CI2 = NULL

# add the two datasets together
dataXL <- rbind(data1, data2)
```

```{r, linear regression Facebook use}
# which type of facebook use can explain social comparison the best?
fit <- lm(COMF ~ 1 + MSFUP + MSFUaprivate + MSFUapublic, dataXL)
summary(fit)
Anova(fit)
coef(fit)
```

```{r, model with path CSS -> RSES}
# COMF -> CSS -> RSES -> Stress + Anxiety + Depression 
model3 <- '# direct effect 
              DASS_stress + DASS_anxiety + DASS_depression ~ c*COMF
           # indirect effect 1
              RSES ~ a1*COMF
              DASS_stress + DASS_anxiety + DASS_depression ~ b1*RSES
           # indirect effect 2
              CSS ~ a2*COMF
              DASS_stress + DASS_anxiety + DASS_depression ~ b2*CSS
           # indirect effect 3
              RSES ~ b3*CSS
           # indirect effect 1
              a1b1 := a1*b1
           # indirect effect 2
              a2b2 := a2*b2 
           # indirect effect 3
              a2b3b1 := a2*b3*b1
           # total effect 
              total := c + (a1*b1) + (a2*b2) + (a2*b3*b1)'
fit3 <- sem(model3, data = dataXL, se = 'bootstrap', set.seed(1))
summary(fit3, ci = TRUE, standardized = TRUE)
```
```{r, model without path CSS -> RSES}
# COMF -> CSS -> RSES -> Stress + Anxiety + Depression 
model4 <- '# direct effect 
              DASS_stress + DASS_anxiety + DASS_depression ~ c*COMF
           # indirect effect 1
              RSES ~ a1*COMF
              DASS_stress + DASS_anxiety + DASS_depression ~ b1*RSES
           # indirect effect 2
              CSS ~ a2*COMF
              DASS_stress + DASS_anxiety + DASS_depression ~ b2*CSS
           # indirect effect 1
              a1b1 := a1*b1
           # indirect effect 2
              a2b2 := a2*b2 
           # total effect 
              total := c + (a1*b1) + (a2*b2)'
fit4 <- sem(model4, data = dataXL, se = 'bootstrap', set.seed(1))
summary(fit4, ci = TRUE, standardized = TRUE)
```

```{r, comparing models: likelihood ratio test}
# log-likelihood values 
LL1 <- summary(fit3)$LogLik
LL2 <- summary(fit4)$LogLik
# likelihood ratio test 
LRtest <- anova(fit3, fit4)
print(LRtest)
```


The likelihood ratio test compares the goodness of fit of two nested regression models. 
H0: The full model and the nested model fit the data equally well. Thus, you should use the nested model
Ha: The full model fits the data significantly better than the nested model. Thus, you should use the full model 

In our analysis, the p-value < .001, therefore we can reject the null hypothesis and we can conclude that the full model offers a significantly better fit 

```{r, Visualization Mediation Model with Path CSS -> RSES}
data <- c(0, "'0.034'", 0,"'-0.384*'",
          0, 0, 0,0,
          "'-0.514*'", "'0.077*'", 0,"'0.030'",
          0, "'0.466*'", 0,0)
M <- matrix (nrow=4, ncol=4, byrow = TRUE, data=data)

plot2 <- plotmat (M, pos=c(1,2,1),
                  name= c("Global \nSelf-Esteem","Social Comparison \non Facebook", "Despression, \nAnxiety, \nStress Symptoms", "Contingent \nSelf-Esteem"), box.type = "rect", box.size = 0.1, box.prop=0.5, shadow.size = 0,
                  arr.pos = 0.4, curve = 0)
```
```{r, Visualization Mediation Model without Path CSS -> RSES}
data <- c(0, "'-0.145*'", 0,0,
          0, 0, 0,0,
          "'-0.516*'", "'0.077*'", 0,"'0.030'",
          0, "'0.466*'", 0,0)
M <- matrix (nrow=4, ncol=4, byrow = TRUE, data=data)

plot2 <- plotmat (M, pos=c(1,2,1),
                name= c("Global \nSelf-Esteem","Social Comparison \non Facebook", "Despression, \nAnxiety, \nStress Symptoms", "Contingent   \nSelf-Esteem"), 
                box.type = "rect", box.size = 0.1, box.prop=0.5, shadow.size = 0,
                arr.pos = 0.5, curve = 0)
```

```{r, power analysis}
wp.mediation(n = 675, a = 0.2, b = 0.2, varx = 1, vary = 1, varm = 1, alpha = 0.05)
```